---
title: "Hw3_p8105"
author: "Jingwei Ren"
date: "10/13/2018"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(patchwork)

knitr::opts_chunk$set(echo = TRUE)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

##problem1
First, do some data cleaning:

format the data to use appropriate variable names;
focus on the “Overall Health” topic
include only responses from “Excellent” to “Poor”
organize responses as a factor taking levels ordered from “Excellent” to “Poor”

```{r, clean_up}
brfss = brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health" & (response == "Excellent" | response == "Very good" |
                                       response == "Good" | response == "Fair" | 
                                       response == "Poor")) %>% 
  mutate(response = factor(response, level = c("Excellent","Very good", "Good", "Fair", "Poor")))
```

Using this dataset, do or answer the following (commenting on the results of each):

In 2002, which states were observed at 7 locations?
```{r, filter}
brfss %>% 
  filter(year == 2002) %>% 
  group_by(locationabbr) %>% 
  summarize(n_location = n_distinct(locationdesc)) %>% 
  filter(n_location == 7)
```
CT,FL and NC were observed at 7 locations.
